Realizing temporal graphs from fastest travel times

### 2023-02-02 ICALP23-RealizingTemporalGraphs.tex
Finished NP-hardness construction

\begin{proof}
	We present a polynomial-time reduction from the NP-hard problem 3-SAT~\cite{Karp1972Reducibility}. Here, we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables). We construct an instance $D^\phi$ of \deltaExact\ as follows.

 We start by describing the vertex set of the underlying graph $G$ of  $D^\phi$.
\begin{itemize}
\item For each variable $x$ in $\phi$, we create three variable vertices $x, x^T, x^F$.
\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
\item We add one additional super vertex $v$.
\end{itemize}
Next, we describe the edge set of $G$.
\begin{itemize}
\item For each variable $x$ in $\phi$ we add the following five edges: 
$x x^T, x x^F, x^T x^F, x^T v$ and $ x^Fv$.
\item For each pair of variables $x,y$ in $\phi$ with $x\neq y$ we add the following four edges: 
$x^T y^T, x^Ty^F, x^Fy^T$ and $x^Fy^F$.
\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x$ appear in $c$. If $x$ appears non-negated in $c$ we add edge $c x^T$. 
If $x$ appears negated in $c$ we add edge $c x^F$.
\end{itemize}
This finishes the construction of $G$.
For an example see~\cref{fig:NP-example}.

Now we specify the distances in the matrix $D^\phi$ between all vertex pairs.
For the sake of simplicity we write $D^\phi _{x,y}$ as $d(x,y)$,
where $x,y$ are two vertices. 
We start by setting the value of $d(x,y) = 1$ where $x$ and $y$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x$ in $\phi$ we specify the following distance to the super vertex $v$:
    $d(x,v)=2$. %, $d(x_2,v)=3$.

    \item For each clause $c$ in $\phi$ we specify the following distance to the super vertex $v$:
    $d(c,v)=2$
    \item Let $x$ be a variable that appears in clause $c$, then  we specify the following distance:
    $d(c,x)=2$.
    If $x$ appears non-negated in $c$ we specify the following distance:
    $d(c,x^F)=2$.
    If $x$ appears negated in $c$ we specify the following distance:
    $d(c,x^T)=2$.
    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distance:
    $d(c,x^T)=d(c,x^F)=2$.
\end{itemize}
All distances between non-adjacent vertex pairs that are not defined above are set to $\infty$.

This finishes the construction of an instance $D^\phi$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $D^\phi$ is a yes-instance if and only if $\phi$ is satisfiable.

We construct a satisfying assignment for $\phi$ as follows. For each variable $x$, if $\lambda(x x^T)=\lambda(x^T v)$, then we set $x$ to \textsc{True}, otherwise we set $x$ to \textsc{False}.

To show that this yields a satisfying assignment, we need to show some following properties of $\lambda$.
First, observe that adding some integer $t$ to all time labels does not change the duration of any temporal path. Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$, then there is a shortest path from $u$ to $w$ in $G$ such that $\lambda$ puts consecutive time labels on the edges of that shortest path.

Let $\lambda(x x^T)=t$ and $\lambda(x x^F)=t'$, for an arbitrary variable $x$. 
If both $\lambda(x^T v)\neq t+1$ and $\lambda(x^F v)\neq t'+1$, then $d(x,v)>2$, which is a contradiction. 
Thus, for every variable $x$, we have that $\lambda(x^T v)= t+1$ or $\lambda(x^F v)= t'+1$ (or both). 
In particular, this means that if $\lambda(x x^F)=\lambda(x^F v)$, then we set $x$ to \textsc{False}, since in this case $\lambda(x x^T)\neq\lambda(x^T v)$.

Now assume for contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. Recall that we require $d(c,v)=2$. Hence, we must have a temporal path consisting of two edges from $c$ to $v$ such that the two edges have consecutive labels. By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
Assume w.l.o.g\ that $x$ appears in $c$ non-negated (the case of a negated appearance of $x$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x^T$. 
Then we have that $\lambda(c x^T)=\lambda(x^T v)-1$. Furthermore, since $d(c,x)=2$ we also have that $\lambda(c x^T)=\lambda(x x^T)-1$. It follows that $\lambda(x x^T)=\lambda(x^T v)$. However, this implies that $x$ is set to \textsc{True} in the satisfying assignment and thus the clause $c$ is satisfied, a contradiction.

We construct a labeling $\lambda$ as follows.
\begin{itemize}
    \item All edges incident with a clause vertex $c$ obtain label one.
    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
    \item If variable $x$ is set to \textsc{True}, we set $\lambda(x^F v)=3$.
    \item If variable $x$ is set to \textsc{False}, we set $\lambda(x^T v)=3$.
    \item We set the labels of all other edges to two.
\end{itemize}

Next, we verify that all distances are realized.
\begin{itemize}
    \item For each variable $x$ in $\phi$ we have $d(x,v)=2$:

    If $x$ is set to \textsc{True}, then there is a temporal path from $x$ to $v$ via $x^F$ such that $\lambda(x x^F)=2$ and $\lambda(x^F v)=3$. If $x$ is set to \textsc{False}, then there is a temporal path from $x$ to $v$ via $x^T$ such that $\lambda(x x^T)=2$ and $\lambda(x^T v)=3$.

    \item For each clause $c$ in $\phi$ we have that $d(c,v)=2$:

    Since we have a satisfying assignment there is a variable $x$ appearing in $c$ that is set to a truth-value that satisfies $c$. If $x$ appears non-negated in $c$ (and hence is set to \textsc{True}), then there is a temporal path from $c$ to $v$ through $x^T$ such that $\lambda(c x^T)=1$ and $\lambda(x^T v)=2$. If $x$ appears negated in $c$ (and hence is set to \textsc{False}), then there is a temporal path from $c$ to $v$ through $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x^F v)=2$.
    \item Let $x$ be a variable that appears in clause $c$.
    If $x$ appears non-negated in $c$ we have $d(c,x)=d(c,x_F)=2$:

    There is a temporal path from $c$ to $x$ via $x^T$ and also a temporal path from $c$ to $x^F$ via $x^T$ such that $\lambda(c x^T)=1$ and $\lambda(x x^T)=\lambda(x^T x^F)=2$.

    If $x$ appears negated in $c$ we have $d(c,x)=d(c,x_T)=2$:

    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$.
    \item Let $x$ be a variable that does \emph{not} appear in clause $c$, then we have $d(c,x^T)=d(c,x^F)=2$:

    Let $y$ be a variable that appears non-negated in $c$ (the case where $y$ appears negated is symmetrical). Then there is a temporal path from $c$ to $x^T$ via $y^T$ and also a temporal path from $c$ to $x^F$ via $y^T$ such that $\lambda(c y^T)=1$ and $\lambda(y^T x^T)=\lambda(y^T x^F)=2$.
\end{itemize}
Lastly, we show that all non-adjacent vertex pairs $u,w$ with $d(u,w)=\infty$ are not temporally connected in $(G,\lambda)$.
\begin{itemize}
\item For all pairs of clause vertices $c,c'$ we have $d(c,c')=\infty$: 
\todo[inline]{New matrix entries D for period Delta: d(c,c')=Delta+1 (using three edges, with labels L, L+1, L).}

Since all edges incident with clause vertices have label one and clause vertices are pairwise non-adjacent, there cannot be a temporal path from one clause vertex to another.
\item For all variable vertices $x$ and clause vertices $c$ we have $d(x,c)=\infty$:
\todo[inline]{New matrix entries D for period Delta: if x appears (negated or not) in c, then d(x,c)=Delta (using two edges, with label L+1, L). Otherwise D(x,c)=2Delta (using three edges, with labels L, L, L-1).}

Since all edges incident with variable vertices $x$ have label two and all edges incident with clause vertices $c$ have label one, there cannot be a temporal path from a variable vertex $x$ to a clause vertex $c$.
\item For all pairs of variable vertices $x,y$ we have $d(x,y)=\infty$:
\todo[inline]{New matrix entries D for period Delta: d(x,y)=2Delta+1 (using three edges, each with the same label).}

Since all edges incident with variable vertices $x$ have label two and variable vertices $x$ are pairwise non-adjacent, there cannot be a temporal path from one variable vertex to another.
\item For all pairs of variable vertices $x,y$ we have $d(y^T,x)=d(y^F,x)=\infty$:
\todo[inline]{New matrix entries D for period Delta: $d(y^T,x)=d(y^F,x)=Delta+1$ (using two edges, with equal labels).}

Since all edges incident with variable vertices $x$ have label two and all edges incident with variable vertices $y^T, y^F$ have labels two or three and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from a variable vertex $y^T$ or $y^F$ to variable vertex $x$.
\item For all pairs of variable vertices $x,y$ we have $d(x,y^T)=d(x,y^F)=\infty$:
\todo[inline]{New matrix entries D for period Delta: $d(x,y^T)=d(x,y^F)=Delta+1$ (using two edges, with equal labels).}

Observe that edges incident with $y^T, y^F$ that have label three connect $y^T, y^F$ to $v$. Furthermore, $v$ has distance two from $x$ in the underlying graph $G$. Since all edges incident with variable vertices $x$ have label two, there is no temporal path starting at $x$ and arriving at $v$ at time two, that could then continue to $y_T$ or $y_F$ using an edge with label three. Hence, there is no temporal path from $x$ to $y^T, y^F$ using an edge with label three. Since all edges incident with $x$ have label two and variable vertices $x$ are non-adjacent to variable vertices $y^T,y^F$, there cannot be a temporal path from variable vertex $x$ to variable vertex $y^T$ or $y^F$.
\item For all variable vertices $x$ and clause vertices $c$ we have $d(v,x)=d(v,c)=\infty$:
\todo[inline]{New matrix entries D for period Delta: d(v,x)=Delta (using two edges, with labels L+1,L). 
New matrix entries D for period Delta: d(v,c)=Delta (using two edges, with labels L,L-1).}

All edges incident with $v$ have labels two or three. All edges incident with $x$ have label two and all edges incident with $c$ have label one. We immediately have that there is no temporal path from $v$ to $c$. Furthermore, since $x$ and $v$ are non-adjacent, we also have that there is no temporal path from $v$ to $x$.
\end{itemize}
%
\begin{figure}[htb]
	\noindent
	\makebox[\textwidth]{
		\centering
\begin{tikzpicture}%[xscale=2]

@@

	\draw [dotted] (x3f) [out=30,in=150] to (x4t);
	\draw [dotted] (x3f) [out=30,in=150] to (x4f);
\end{tikzpicture}
}
\caption{Example of the temporal graph $(G_\phi,\lambda)$ from the NP-hardness reduction, 
	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neg j$) with a dotted line.
Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
where all unlabeled edges get the label $2$.
\label{fig:NP-example}}
\end{figure}
\end{proof}

@@

    \subparagraph{Verification Gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
    \begin{itemize}
        \item We have one vertex $y^i$, one vertex $v^i_0$, and $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$.
        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{n}$ and $n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{n}$.
        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n+3$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{n+3}$.
    \end{itemize}
    We add the following edges. We add edge $\{y^i,v^i_0\}$.
    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.

>>>>

\begin{proof}
	We present a polynomial-time reduction from the NP-hard problem NAE 3-SAT~\cite{Schaefer1978complexity}. Here we are given a formula $\phi$ in conjunctive normal form, where each clause contains exactly 3 literals (with three distinct variables).
    A NAE clause evaluates to \textsc{True} iff not all of its literals are equal.
    We construct an instance $D^\phi$ of \deltaExact\ as follows.

 We start by describing the vertex set of the underlying graph $G$ of  $D^\phi$.
\begin{itemize}
\item For each variable $x_i$ in $\phi$, we create three variable vertices $x_i, x_i^T, x_i^F$.
\item For each clause $c$ in $\phi$, we create one clause vertex $c$.
\item We add one additional super vertex $v$.
\end{itemize}
Next, we describe the edge set of $G$.
\begin{itemize}
\item For each variable $x_i$ in $\phi$ we add the following five edges: 
$x_i x_i^T, x_i x_i^F, x_i^T x_i^F, x_i^T v$ and $ x_i^Fv$.
\item For each pair of variables $x_i,x_j$ in $\phi$ with $i \neq j$ we add the following four edges: 
$x_i^T x_j^T, x_i^Tx_j^F, x_i^Fx_j^T$ and $x_i^Fx_j^F$.
\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x_i$ appear in $c$. If $x_i$ appears non-negated in $c$ we add edge $c x_i^T$. 
If $x_i$ appears negated in $c$ we add edge $c x_i^F$.
\end{itemize}
This finishes the construction of $G$.
For an example see~\cref{fig:NP-example}.

%
\begin{figure}[htb]
	\noindent
	\makebox[\textwidth]{
		\centering
\begin{tikzpicture}%[xscale=2]

@@

	\draw [dotted] (x3f) [out=30,in=150] to (x4t);
	\draw [dotted] (x3f) [out=30,in=150] to (x4f);
\end{tikzpicture}
}
\caption{Example of the temporal graph $(G_\phi,\lambda)$ from the NP-hardness reduction, 
	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with a dotted line.
Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
where all unlabeled edges get the label $2$.
\label{fig:NP-example}}
\end{figure}
%
Now we specify the distances in the matrix $D^\phi$ between all vertex pairs.
For the sake of simplicity we write $D^\phi _{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following distances:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following distances:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following distances:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following distances:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following distances:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following distances:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following distances:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following distances:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of an instance $D^\phi$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $D^\phi$ is a yes-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.

We construct a satisfying assignment for $\phi$ as follows. For each variable $x_i$, 
if $\lambda(x_i x_i^T)=\lambda(x_i^T v)$, then we set $x_i$ to \textsc{True}, otherwise we set $x_i$ to \textsc{False}.

To show that this yields a satisfying assignment, we need to prove some properties of the labeling $\lambda$.
First, observe that adding an integer $t$ to all time labels does not change the duration of any temporal paths. 
Second, observe that if for two vertices $u,w$ we have that $d(u,w)$ equals the distance between $u$ and $w$ in $G$
(\ie the duration of the fastest temporal path from $u$ to $w$ equals the distance of the shortest path between $u$ and $w$), 
then there is a shortest path $P$ from $u$ to $w$ in $G$ such that 
the labeling $\lambda$ assigns consecutive time labels to the edges of $P$.

Let $\lambda(x_i x_i^T)=t$ and $\lambda(x_i x_i^F)=t'$, for an arbitrary variable $x_i$. 
If both $\lambda(x_i^T v)\neq t+1$ and $\lambda(x_i^F v)\neq t'+1$, then $d(x_i,v)>2$, which is a contradiction. 
Thus, for every variable $x_i$, we have that $\lambda(x_i^T v)= t+1$ or $\lambda(x_i^F v)= t'+1$ (or both). 
In particular, this means that if $\lambda(x_i x_i^F)=\lambda(x_i^F v)$, then we set $x_i$ to \textsc{False}, since in this case $\lambda(x_i x_i^T)\neq\lambda(x_i^T v)$.

Now assume for a contradiction that the described assignment is not satisfying. Then there exists a clause $c$ that is not satisfied. 
Suppose that $x_1, x_2, x_3$ are three variables that appear in $c$.
Recall that we require $d(c,v)=2$ and $d(v,c)=\Delta -1$. 
The fact that $d(c,v)=2$ implies that we must have a temporal path consisting of two edges from $c$ to $v$, 
such that the two edges have consecutive labels. 
By construction of $G$ there are three candidates for such a path, one for each literal of $c$. 
Assume w.l.o.g\ that $x_1$ appears in $c$ non-negated (the case of a negated appearance of $x_1$ is symmetrical) and that the temporal path realizing $d(c,v)=2$ goes through vertex $x_1^T$. 
Let us denote with $t = \lambda(x_1^T v)$.
It follows that $\lambda(x_1^T c)=\lambda(x_1^T v)-1 = t - 1$.
Furthermore, since $d(c,x_1)=2$ we also have that $\lambda(x_1^T c)=\lambda(x_1 x_1^T)-1$. 
Therefore $\lambda(x_1 x_1^T)=\lambda(x_1^T v) = t$. 
Which implies that $x_1$ is set to \textsc{True}.
%
Let us observe paths from $v$ to $c_1$.
We know that $d(v,c)=\Delta -1$.
The underlying path of the fastest temporal path from $v$ to $c$, that goes through $x_1^T$ is the path $P = (v,x_1^T,c)$.
Since $\lambda(x_1^Tc) > \lambda(x_1^T v)$ we get that the duration of the temporal path $(P,\lambda)$ is equal to 
$d(P,\lambda)= (\Delta + t-1) - t + 1 = \Delta$.
This implies that
the fastest temporal path from $v$ to $c$ is not $(P,\lambda)$ and therefore does not pass through $x_1^T$.
Since there are only two other vertices connected to $c$, 
we have only two other edges incident to $c$, that can be used on a fastest temporal path
$v$ to $c$.
Suppose now w.l.o.g\ that also $x_2$ appears in $c$ non-negated (the case of a negated appearance of $x_2$ is symmetrical) and that the temporal path realizing $d(v,c)=\Delta$ goes through vertex $x_2^T$.
Let us denote with $t' = \lambda(x_2^T v)$.
Since the fastest temporal path from $v$ to $c$ is of the duration $\delta - 1$,
and the edge $x_2^T c$ is the only edge incident to vertex $c$ and edge $ x_2^T v$,
it follows that $\lambda(x_2^T c) \geq \lambda(x_2^T v) - 2 = t' - 2$.
Since $d(x_2,v) = 2$ it follows that $\lambda(x_2 x_2^T) = \lambda (x_2^T v) - 1 = t' - 1$.
Knowing this and the fact that $d(x_2,c)=2$, we get that $\lambda(x_2^T c)$ must be equal to $t'-2$.
Therefore the fastest temporal path from $v$ to $c$ passes through edges $ x_2^Tv$ and $x_2^Tc$.
In the above we have also determined that $\lambda(x_2x_2^T) \neq \lambda ( x_2^Tv)$,
which implies that $x_2$ is set to \textsc{True}.
But now we have that $x_1,x_2$ both appear in $c$, where one of them is \textsc{True}, while the other is \textsc{False},
which implies that the clause $c$ is satisfied, a contradiction.

We construct a labeling $\lambda$ as follows.
\begin{itemize}
    \item All edges incident with a clause vertex $c$ obtain label one.
    %\item For each variable $x$, we set $\lambda(\{x^T,x^F\})=1$.
    \item If variable $x_i$ is set to \textsc{True}, we set $\lambda(x_i^F v)=3$.
    \item If variable $x_i$ is set to \textsc{False}, we set $\lambda(x_i^T v)=3$.
    \item We set the labels of all other edges to two.
\end{itemize}
For an example of the constructed temporal graph see~\cref{fig:NP-example}.
We now verify that all distances are realized.
\begin{itemize}
    \item For each variable $x_i$ in $\phi$ we have to check that $d(x_i,v)=2$
    and $d(v,x_i)=\Delta$.

    If $x_i$ is set to \textsc{True}, then there is a temporal path from $x_i$ to $v$ via 
    $x_i^F$ of duration $2$, since
    $\lambda(x_i x_i^F)=2$ and $\lambda(x_i^F v)=3$.
    For a temporal path from $v$ to $x_i$ we observe the following.
    The only possible labels to leave the vertex $v$ are $2$ and $3$, which take us from $v$ to $x_j^T$ or $x_j^F$ of some variable $x_j$.
    The only two edges incident to $x_i$ have labels $2$, therefore the fastest path from $v$ to $x_i$
    cannot finish before the time $\Delta + 2$.
    The fastest way to leave $v$ and enter to $x_i$ would then be to leave $v$ at edge $x_i^Fv$ with label $3$,
    and continue to $x_i$ at time $\Delta + 2$,
    which gives us the desired duration $\Delta$.

    If $x_i$ is set to \textsc{False}, then, by similar arguing, 
    there is a temporal path from $x_i$ to $v$ via $x_i^T$ of duration $2$,
    and a temporal path from $v$ to $x_i$, through $x_i^F$ of duration $\Delta$.

    \item For each clause $c$ in $\phi$ we have to check that $d(c,v)=2$
    and $d(v,c)=\Delta - 1$:

    Suppose $x_i,x_j,x_k$ appear in $c$.
    Since we have a satisfying assignment at least one of the literals in $c$ is set to \textsc{True} and at least one to \textsc{False}. 
    Suppose $x_i$ is the variable of the literal that is \textsc{True} in $c$,
    and $x_j$ is the variable of the literal that is \textsc{False} in $c$.
    Let $x_i$ appear non-negated in $c$ and is therefore set to \textsc{True} (the case when $x_i$ appears negated in $c$ and is set to \textsc{False} is symmetric).
    Then there is a temporal path from $c$ to $v$ through $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i^T v)=2$. 
    Let $x_j$ appear non-negated in $c$ and is therefore set to \textsc{False} 
    (the case when $x_j$ appears negated in $c$ and is set to \textsc{True} is symmetric).
    Then there is a temporal path from $v$ to $c$ through $x_j^T$ such that $\lambda(x_j^T v)=3$ and $\lambda(x_j^T c)=1$,
    which results in a temporal path from $v$ to $c$ of duration $\Delta -1$.

    \item Let $x_i$ be a variable that appears in clause $c$.
    If $x_i$ appears non-negated in $c$ we have to check that $d(c,x_i)=d(c,x_i^F)=2$
    and $d(x_i,c)=d(x_i^F,c)= \Delta$.

    There is a temporal path from $c$ to $x_i$ via $x_i^T$ and also a temporal path from $c$ to $x_i^F$ via $x_i^T$ such that $\lambda(x_i^T c)=1$ and $\lambda(x_i x_i^T)=\lambda(x_i^T x_i^F)=2$,
    which proves the first equality.
    There are also the following two temporal paths,
    first, from $x_i$ to $c$ through $x_i^T$ and
    second, from $x_i^F$ to $c$ through $x_i^T$.
    Both of the temporal paths start on the edge with label $2$, as 
    $\lambda(x_i x_i^T) = \lambda (x_i^T x_i^F)=2$ and 
    finish on the edge with label $1$, as $\lambda(x_i^T c) = 1$.

    If $x$ appears negated in $c$ we have to check that 
    $d(c,x_i)=d(c,x_i^T)=2$
    and $d(x_i,c)=d(x_i^T,c)= \Delta$.

    There is a temporal path from $c$ to $x$ via $x^F$ and also a temporal path from $c$ to $x^T$ via $x^F$ such that $\lambda(c x^F)=1$ and $\lambda(x x^F)=\lambda(x^T x^F)=2$,
    which proves the first inequality.
    There are also the following two temporal paths,
    first, from $x_i$ to $c$ through $x_i^F$ and
    second, from $x_i^T$ to $c$ through $x_i^F$.
    Both of the temporal paths start on the edge with label $2$, as 
    $\lambda(x_i x_i^F) = \lambda (x_i^T x_i^F)=2$ and 
    finish on the edge with label $1$, as $\lambda(x_i^F c) = 1$.
    Which proves the second equality.

    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we have to check that
    first,
    $d(c,x_i^T)=d(c,x_i^F)=2$,
    second, $d(x_i^T, c) = d(x_i^F,c)=\Delta$,
    third, $d(x_i,c)=\Delta$,
    and fourth $d(c,x_i)=2 \Delta + 2$.

    Let $x_j$ be a variable that appears non-negated in $c$ (the case where $x_j$ appears negated is symmetric). 
    Then there is a temporal path 
    from $c$ to $x_i^T$ via $x_j^T$ and also a temporal path 
    from $c$ to $x_i^F$ via $x_j^T$ such that $\lambda(x_j^T c)=1$ and $\lambda(x_j^T x_i^T)=\lambda(x_j^T x_i^F)=2$,
    which proves the first equality.
    Using the same temporal path in the opposite direction,
    \ie first the edge $x_j^T c$ and then one of the edges $x_j^T x_i^F$ or $x_j^T x_i^T$,
    yields the second equality.
    For a temporal path from $c$ to $x_i$ we traverse the following three edges 
    $x_j^T c, x_j^T x_i^F$ and $x_i^Fx_i$,
    with labels $1, 2, 2$ respectively.
    This proves the second equality.
    Now for the case of a temporal path from $x_i$ to $c$,
    we use the same three edges, but in the opposite direction,
    namely $x_i^Fx_i, x_j^T x_i^F$ and $x_j^T c$,
    again with labels $2, 2, 1$, respectively,
    which proves the last equality.
    Note that all of the above temporal paths are also the shortest possible, 
    and since the labels of first and last edges (of these paths) are unique,
    it follows that we cannot find faster temporal paths.

    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we have to check that
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.

    There is a path from $x_i$ to $x_j$ that passes first through one of the vertices 
    $x_i^T$ or $x_i^F$, 
    and then through one of the vertices $x_j^T$ or $x_j^F$.
    This temporal path is of length $3$, where all of the edges have label $2$,
    which proves the first equality.
    Now, a temporal path from $x_i$ to $x_j^T$ (resp.~$x_j^F$),
    passes through one of the vertices $x_i^T$ or $x_i^F$.
    This path is of length two, where all of the edges have label $2$,
    which proves the second equality.
    Note that all of the above temporal paths are also the shortest possible, 
    and since the labels of first and last edges (of these paths) are unique,
    it follows that we cannot find faster temporal paths.

    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we have to check that
    $d(c_i,c_j)= \Delta + 1$.

    Let $x_k$ be a variable that appears non-negated in $c_i$
    and $x_\ell$ the variable that appears non-negated in $c_j$
    (all other cases are symmetric).
    There is a path of length three from $c_i$ to $c_j$
    that passes first through vertex $x_k^T$ and then through vertex $x_\ell^T$.
    Therefore the temporal path from $c_i$ to $c_j$
    uses the edges $x_k^T c_i, x_\ell ^T c_j, x_k^T x_\ell ^T$, with labels $1,2,1$, respectively,
    which proves the desired equality.
    Note also that this is the shortest path between $c_i$ and $c_j$, and that the first and the last edge must have the label $1$,
    therefore it follows that this is the fastest temporal path.
\end{itemize}
%
\end{proof}

@@

    \subparagraph{Verification Gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
    \begin{itemize}
        \item We have one vertex $y^i$, one vertex $v^i_0$, and $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$.
        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n+3$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{n+3}$.
    \end{itemize}
    We add the following edges. We add edge $\{y^i,v^i_0\}$.
    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.

    Let $1\le j<i$ (skip if $i=1$), let $e_\ell^{j,i}\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{j,i}$. Then we add edge $\{v_{j-1}^i,a^{i,j,\ell}_{1}\}$ and we add edge $\{a^{i,j,\ell}_{5n},u^\ell_{\ell'-1}\}$ between $a^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'-1}$ of the edge selection gadget of color combination $j,i$.
    Furthermore, we add edge $\{v_{j}^i,b^{i,j,\ell}_{1}\}$ and edge $\{b^{i,j,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,j,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
